A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-08-07 manuscript.tex
typos

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials and  software is available at \url{https://janniscodes.github.io/migration-trajectories/}  \citep{KreienkampTBD}. Protocols, materials, data, and code are available at \url{https://osf.io/TBA} \citep{KreienkampTBD}. The preregistration of our analysis can be accessed as part of our Open Science Framework repository \citep{KreienkampTBD}.

>>>>

We have no known conflict of interest to declare. The authors received no specific funding for this work. Materials and  software are available at \url{https://janniscodes.github.io/migration-trajectories/}  \citep{KreienkampTBD}. Materials, data, and code are available at \url{https://osf.io/TBA} \citep{KreienkampTBD}.
